### 2018-01-25 doc/manuscript.Rmd
only one dot size for signif for gee, remove legend

```{r fig_gee_unadj, fig.cap=fig_gee_unadj}
plot_gee_main(gee_unadj_df)
```

```{r fig_gee_adj, fig.cap=fig_gee_adj}
plot_gee_main(gee_adj_df)
```

>>>>

```{r fig_gee_unadj, fig.cap=fig_gee_unadj}
gee_unadj_df %>% 
    mutate(p.value = ifelse(p.value <= 0.05, 0.04, p.value)) %>% 
    plot_gee_main() +
    ggplot2::theme(legend.position = "none")
```

```{r fig_gee_adj, fig.cap=fig_gee_adj}
gee_adj_df %>% 
    mutate(p.value = ifelse(p.value <= 0.05, 0.04, p.value)) %>% 
    plot_gee_main() +
    ggplot2::theme(legend.position = "none")
```
